Random Forests", OAs

### 2025-03-10 src/oa_RF_corrected.Rmd
oa regions
oa regions 10

# [not reproducible despite having the code as the LAD models]
# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.236301  0.3128048  1.211779
#   2     extratrees  3.453903  0.2169766  1.184256
#   5     variance    3.217652  0.3331498  1.233429
#   5     extratrees  3.390341  0.2491582  1.254907
#   8     variance    3.296126  0.3199896  1.241124
#   8     extratrees  3.418875  0.2485125  1.283134
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance
#  and min.node.size = 5.

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "RGN21CD",
                                timevar = "year", 
                                k = k)

>>>>

# [not reproducible despite having the code as the LAD models]
# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.236887  0.3130255  1.212322
#   2     extratrees  3.452335  0.2176573  1.182235
#   5     variance    3.218065  0.3330621  1.233640
#   5     extratrees  3.390579  0.2490956  1.252252
#   8     variance    3.295241  0.3206509  1.240731
#   8     extratrees  3.420014  0.2487011  1.283227
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance
#  and min.node.size = 5.

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD!=i), 
                                spacevar = "RGN11CD",
                                timevar = "year", 
                                k = k)
